\sffamily An EEG-based visual Brain-Computer Interface for gaze-free communication

### 2024-11-15 chapters/stbf_struct.tex
Rework fig 1.1 and fig 1.2

	\begin{figure}
		\includegraphics[width=\linewidth]{figures/stbf_struct/covs.eps}
    \caption[Estimated covariance and inverse covariance.]{Different estimators of the covariance and inverse covariance
			of 100 epochs of data from \textit{Subject 01} for channels
			\textit{Fz}, \textit{Cz}, \textit{Pz}, and \textit{Oz} and time samples between 0.1s and 0.6s.
			Regularized estimators of the inverse covariance exhibit less extreme values and have a sparser structure.
			(\textbf{a,b}) Empirical covariance and inverse covariance matrices.
			(\textbf{c,d}) Shrunk covariance and inverse covariance matrices with $\alpha=0.14$ as
			determined by the closed-form \ac{loocv} method. (\textbf{e,f}) Kronecker-Toeplitz
			structured covariance and inverse covariance matrices.
			(\textbf{g,h}) Spatial Kronecker factor of the Kronecker-Toeplitz structured shrunk estimator and its inverse.
			(\textbf{i,j}) Temporal Kronecker factor of the Kronecker-Toeplitz structured shrunk estimator and its inverse.}
		\label{fig:kronlda-covs}
	\end{figure}

@@

  \begin{figure}
		\includegraphics[width=\linewidth]{figures/stbf_struct/fpi.eps}
    \caption[Average cross-validated \textsc{stbf-struct} accuracy]{%
      Average cross-validated \textsc{stbf-struct} accuracy using
			one trial per block over all 21 subjects
			relative to the number of iterations used to estimate the Kronecker-Toeplitz structured shrunk
			covariance. Error bars represent the first and third quartiles. The
			accuracy does not improve when using more than one iteration.
			(\textbf{a}) Results for 1, 2, and 5 trials using only the first block in each
			training fold for training. (\textbf{b}) Results
			for 1, 2, and 5 trials using
			all nine training blocks in the training folds.
		}
		\label{fig:iterations}
	\end{figure}

>>>>

	\begin{figure}
		%\includegraphics[width=\linewidth]{figures/stbf_struct/covs.eps}
    \begin{subfigure}{\textwidth/4}
		  \includegraphics[width=\linewidth]{figures/stbf_struct/covs-0.eps}
      \caption{}
    \end{subfigure}\hfill%
    \begin{subfigure}{\textwidth/4}
		  \includegraphics[width=\linewidth]{figures/stbf_struct/covs-1.eps}
      \caption{}
    \end{subfigure}\hfill%
    \begin{subfigure}{\textwidth/4}
		  \includegraphics[width=\linewidth]{figures/stbf_struct/covs-2.eps}
      \caption{}
    \end{subfigure}\hfill%
    \begin{minipage}[b]{\textwidth/10}
      \begin{subfigure}{\textwidth}
  		  \includegraphics[width=\linewidth]{figures/stbf_struct/covs-6.eps}
        \caption{}
      \end{subfigure}\vfill%
      \begin{subfigure}{\textwidth}
  		  \includegraphics[width=\linewidth]{figures/stbf_struct/covs-7.eps}
        \caption{}
      \end{subfigure}\hfill%
    \end{minipage}

    \begin{subfigure}{\textwidth/4}
		  \includegraphics[width=\linewidth]{figures/stbf_struct/covs-3.eps}
      \caption{}
    \end{subfigure}\hfill%
    \begin{subfigure}{\textwidth/4}
		  \includegraphics[width=\linewidth]{figures/stbf_struct/covs-4.eps}
      \caption{}
    \end{subfigure}\hfill%
    \begin{subfigure}{\textwidth/4}
		  \includegraphics[width=\linewidth]{figures/stbf_struct/covs-5.eps}
      \caption{}
    \end{subfigure}\hfill%
    \begin{minipage}[b]{\textwidth/10}
      \begin{subfigure}{\textwidth}
  		  \includegraphics[width=\linewidth]{figures/stbf_struct/covs-8.eps}
        \caption{}
      \end{subfigure}\vfill%
      \begin{subfigure}{\textwidth}
  		  \includegraphics[width=\linewidth]{figures/stbf_struct/covs-9.eps}
        \caption{}
      \end{subfigure}\hfill%
    \end{minipage}

    \caption[Estimated covariance and inverse covariance.]{Different estimators of the covariance and inverse covariance
			of 100 epochs of data from \textit{Subject 01} for channels
			\textit{Fz}, \textit{Cz}, \textit{Pz}, and \textit{Oz} and time samples between 0.1s and 0.6s.
			Regularized estimators of the inverse covariance exhibit less extreme values and have a sparser structure.
			(\textbf{a,f}) Empirical covariance and inverse covariance matrices.
			(\textbf{b,g}) Shrunk covariance and inverse covariance matrices with $\alpha=0.14$ as
			determined by the closed-form \ac{loocv} method. (\textbf{c,h}) Kronecker-Toeplitz
			structured covariance and inverse covariance matrices.
			(\textbf{d,e}) Spatial Kronecker factor of the Kronecker-Toeplitz structured shrunk estimator and its inverse.
			(\textbf{i,j}) Temporal Kronecker factor of the Kronecker-Toeplitz structured shrunk estimator and its inverse.}
		\label{fig:kronlda-covs}
	\end{figure}

@@

  \begin{figure}
    \sffamily
    \sansmath
    \begin{subfigure}{\linewidth}
      \input{figures/stbf_struct/fpi-0.pgf}
      \caption{Results for 1, 2, and 5 trials using only the first block in each
      training fold for training.}
    \end{subfigure}
    \smallskip

    \begin{subfigure}{\linewidth}
      \input{figures/stbf_struct/fpi-1.pgf}
      \caption{Results for 1, 2, and 5 trials using all nine training blocks in
      the training folds.}
    \end{subfigure}
    \caption[Average cross-validated \textsc{stbf-struct} accuracy]{%
      Average cross-validated \textsc{stbf-struct} accuracy using
			one trial per block over all 21 subjects
			relative to the number of iterations used to estimate the Kronecker-Toeplitz structured shrunk
			covariance. Error bars represent the first and third quartiles. The
      accuracy does not improve when using more than one iteration.}
		\label{fig:iterations}
	\end{figure}
